Comparison of large-scale citizen science data and long-term study data for phenology modeling

### 2018-10-22 manuscript/supplement_images.tex
first revision (#42)
* progress as of today on revision

includes notes from meeting with Ethan

* progress on revision

* add t-test to figure 4

* add a supp. table with overall aggregate errors for best models

* change the layout of supp images 1 and 2

Before they were all RMSE of train and test data for all
NPN models (S1) and LTER models (S2). Now they are RMSE
for all models of only held out data (S1) and pearson
correlation for all models of only held out data (S2)

* change T* to T_base in all images

* differentat the new cutoff time differences in config

* new sensitivity analysis

\begin{document}
{\Comparison of large-scale citizen science data and long-term study data for phenology modeling \par}

\textit{Shawn D. Taylor, Joan M. Meiners, Kristina Riemer, Michael C. Orr, Ethan P. White}

@@

Supplementary images S1 - S11 and Table S1

@@

\begin{center}
	\centering
		\includegraphics[width=1\textwidth]{parameter_estimates_from_cutoff_sensitivity.png}
	Figure S1
\end{center}

@@

\begin{center}
	\centering
		\includegraphics[width=1\textwidth]{figure_param_comparison_15day_cutoff.png}
	Figure S2
\end{center}

@@

\begin{center}
	\centering
		\includegraphics[width=1\textwidth]{figure_estimate_compare_15day_cutoff.png}
	Figure S3
\end{center}

@@

\begin{center}
	\centering
		\includegraphics[width=1\textwidth]{figure_rmse_metrics_density_plot_15day_cutoff.png}
	Figure S4
\end{center}

@@

\begin{center}
	\centering
		\includegraphics[width=1\textwidth]{supplement_all_model_rmse.png}
	Figure S5
\end{center}

\newpage
%%%%%%%%%%%%%%%%%
%% Figure S6
%%%%%%%%%%%%%%%%%
\textbf{Figure S6}: Pearson correlation coefficients for specific species and phenophases using all combinations of models and data sources. Note that since all predictions from each Naive model are the same pearson's correlation cannot be calculated here. Red X's mark the best performing models for each respective dataset.

@@

\begin{center}
	\centering
		\includegraphics[width=1\textwidth]{supplement_all_model_pearson.png}
	Figure S6
\end{center}

@@

\begin{center}
	\centering
		\includegraphics[width=1\textwidth]{supplement_scenario_absolute_rmse.png}
	Figure S7
\end{center}

@@

\begin{center}
	\centering
		\includegraphics[scale=0.5]{supplement_hubbard_harvard_comparison1.png}
	Figure S8
\end{center}

@@

\begin{center}
	\centering
		\includegraphics[scale=0.5]{supplement_hubbard_harvard_comparison2.png}
	Figure S9
\end{center}

@@

\begin{center}
	\centering
		\includegraphics[scale=0.5]{supplement_select_species_param_comparison1.png}
	Figure S10
\end{center}

@@

\begin{center}
	\centering
		\includegraphics[scale=0.5]{supplement_select_species_param_comparison2.png}
	Figure S11
\end{center}
%%%%%%%%%%%%%%%%%
%% Table S1
%%%%%%%%%%%%%%%%%
\newpage

>>>>

\begin{document}

\Large
Appendix S2

AppendixS2.pdf

Comparison of large-scale citizen science data and long-term study data for phenology modeling

\normalsize
\textit{Shawn D. Taylor, Joan M. Meiners, Kristina Riemer, Michael C. Orr, Ethan P. White}

@@

Supplementary images S1 - S11 and Tables S1-S2

@@

\begin{center}
	\centering
		\includegraphics[width=1\textwidth]{figure_s1_parameter_estimates_from_cutoff_sensitivity.png}
	Figure S1
\end{center}

@@

\begin{center}
	\centering
		\includegraphics[scale=0.7]{figure_s2_param_comparison.png}
	Figure S2
\end{center}

@@

\begin{center}
	\centering
		\includegraphics[width=1\textwidth]{figure_s3_estimate_compare.png}
	Figure S3
\end{center}

@@

\begin{center}
	\centering
		\includegraphics[width=1\textwidth]{figure_s4_rmse_metrics_density_plot.png}
	Figure S4
\end{center}

@@

\begin{center}
	\centering
		\includegraphics[width=1\textwidth]{figure_s5_all_model_rmse.png}
	Figure S5
\end{center}

\newpage
%%%%%%%%%%%%%%%%%
%% Figure S6
%%%%%%%%%%%%%%%%%
\textbf{Figure S6}: Pearson correlation coefficients for specific species and phenophases using all combinations of models and data sources. Note that since all predictions from each Naive model are the same the Pearsons correlation cannot be calculated here. Red X's mark the best performing models for each respective dataset.

@@

\begin{center}
	\centering
		\includegraphics[width=1\textwidth]{figure_s6_all_model_pearson.png}
	Figure S6
\end{center}

@@

\begin{center}
	\centering
		\includegraphics[width=1\textwidth]{figure_s7_scenario_absolute_rmse.png}
	Figure S7
\end{center}

@@

\begin{center}
	\centering
		\includegraphics[scale=0.5]{figure_s8_hubbard_harvard_comparison1.png}
	Figure S8
\end{center}

@@

\begin{center}
	\centering
		\includegraphics[scale=0.5]{figure_s9_hubbard_harvard_comparison2.png}
	Figure S9
\end{center}

@@

\begin{center}
	\centering
		\includegraphics[scale=0.5]{figure_s10_select_species_param_comparison1.png}
	Figure S10
\end{center}

@@

\begin{center}
	\centering
		\includegraphics[scale=0.5]{figure_s11_select_species_param_comparison2.png}
	Figure S11
\end{center}
%%%%%%%%%%%%%%%%%
%% Table S1
%%%%%%%%%%%%%%%%%
\newpage

### 2018-10-22 manuscript/supplement_methods.tex
finalize supplement/appendix

\usepackage{graphicx}
\usepackage{a4wide}
\usepackage{lineno}
    \linenumbers
%\usepackage{setspace}
%  \doublespacing
\usepackage[document]{ragged2e}

@@

{\Comparison of large-scale citizen science data and long-term study data for phenology modeling \par} \newline

\textit{Shawn D. Taylor, Joan M. Meiners, Kristina Riemer, Michael C. Orr, Ethan P. White} \newline

{\Large \textbf{Supplementary materials}} \newline
Methods describing processing of the 4 LTER datasets

>>>>

\usepackage{graphicx}
\usepackage{a4wide}
\usepackage{lineno}
%    \linenumbers
%\usepackage{setspace}
%  \doublespacing
\usepackage[document]{ragged2e}

@@

Appendix S1

AppendixS1.pdf

\Large
Comparison of large-scale citizen science data and long-term study data for phenology modeling

\normalsize
\textit{Shawn D. Taylor, Joan M. Meiners, Kristina Riemer, Michael C. Orr, Ethan P. White}

\textbf{\large Supplementary materials}

Methods describing processing of the 4 LTER datasets
